---
title: "Generate decision table for a single or multiple design(s)"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Generate decision table for a single or multiple design(s)}
  %\VignetteEngine{knitr::rmarkdown} 
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE,
  collapse = TRUE
)
```

In this vignette we will demonstrate how to use `FIND` package to generate decision tables for a single or multiple designs. 

Begin by loading the `FIND` library and dependencies:

```{r}
library(FIND)
# Dependencies
library(ggplot2)
library(dplyr)
library(grid)
library(gridExtra)
library(gtable)
```

```{r}
# Main directory
mainDir <- "/Users/oliviazhang/Desktop/"

# library(miceadds)
# source.all(paste0(mainDir, "/FIND/R"))
```


We now turn our attention toward generate decision tables for the design(s) we chose. This involves two steps. 

First, we call the `get.decision.x` functions, where we can replace `x` with the design names. The function will return the dosing decisions (E, S, D or DU) for the user-specified designs. 

For example:

```{r}
decision_i3 <- get.decision.i3(pT = 0.25,
                               EI = c(0.2,0.3),
                               npatients = 12)

decision_boin <- get.decision.b(pT = 0.25,
                                EI = c(0.15,0.35),
                                npatients = 12)

decision_3 <- get.decision.3(npatients = 12)
```

Next, we call the `generate_decision_table` function, which will automatically generate the decision table. 

```{r}
plot <- generate_decision_table(#`3+3` = decision_3,
                                `BOIN` = decision_boin)
                                #`i3+3` = decision_i3)
```

We can also save the plot the local directory:
```{r}
# #Create a new directory named “Results”
# new.folder <- "Results"
# dir.create(file.path(mainDir, new.folder))
# #Create a new sub-directory named “Decision Tables”
# new.subfolder <- "Decision Tables"
# dir.create(file.path(mainDir, new.folder, new.subfolder))
# 
# ggsave(paste0(file.path(mainDir, new.folder, new.subfolder),"/decision_table.jpg"),
#        width = 18,
#        height = 8,
#        plot)
```
 
   
