---
title: "Obtain operating characteristics for a single or multiple design(s)"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Obtain operating characteristics for a single or multiple design(s)} 
  %\VignetteEngine{knitr::rmarkdown} 
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE
)
```

In this vignette we will demonstrate how to use `FIND` package to compare the operating characteristics for a single or multiple designs. 

Begin by loading the `FIND` library and dependencies:

```{r}
library(FIND)
# Dependencies
library(ggplot2)
library(dplyr)
library(grid)
library(gridExtra)
library(gtable)
```

```{r}
# Main directory
mainDir <- "/Users/oliviazhang/Desktop/"

# library(miceadds)
# source.all(paste0(mainDir, "/FIND/R"))
```
We provide several commonly used simulation scenarios.

View by calling the `load.true` function:
```{r}
load.true(pT = 0.25)   
```

We will use the scenarios provided in FFP-BOIN submission:
```{r}
#Load the true toxicity rates
p.true <- load.true(pT = 0.25)[["FFP-BOIN provided"]][["p.true"]]
p.true
```

```{r}
#Load the true MTD
load.true(pT = 0.25)[["FFP-BOIN provided"]][["mtd.true"]]
```

```{r}
# We need to specify which dose(s) is the true MTD for each scenario 
# We will set up the following matrix:
# Each row represents one scenario,
# and 1 indicates that the dose is the true MTD for that scenario
mtd.true <- matrix(c(1,0,0,0,0,0,
                     0,1,0,0,0,0,
                     0,0,1,0,0,0,
                     0,0,0,1,0,0,
                     0,0,0,0,1,0,
                     0,0,0,0,0,1,
                     0,0,0,0,0,0,
                     1,0,0,0,0,0), nrow = 8, ncol = 6, byrow = T)
```

We now turn our attention toward obtaining the operating characteristic for the design(s) we chose. This involves two steps. 

First, we call the `run.sim.x` functions, where we can replace `x` with the design names. The function will run the simulations and return operating charactertistics for the user-specified designs. 

For example:

```{r}
# Run simulations for the 3+3 design
oc_3plus3 <- run.sim.3(p.true = p.true,
                       mtd.true = mtd.true, 
                       startdose = 1,
                       ntrial = 5000,
                       seed = 6)

# Run simulations for the BOIN design
oc_boin <- run.sim.b(p.true = p.true,
                     mtd.true = mtd.true, 
                     pT = 0.25,
                     EI = c(0.15,0.35),
                     ncohort = 12,
                     cohortsize = 3,
                     startdose = 1,
                     DU.pp = 0.95,
                     n.earlystop = 12,
                     extrasafe = F,
                     ntrial = 5000,
                     seed = 6)

# Run simulations for the i3+3 design
oc_i3plus3 <- run.sim.i3(p.true = p.true,
                         mtd.true = mtd.true, 
                         pT = 0.25,
                         EI = c(0.2,0.3),
                         ncohort = 12,
                         cohortsize = 3,
                         startdose = 1,
                         DU.pp = 0.95,
                         #n.earlystop = 12,
                         extrasafe = T,
                         ntrial = 5000,
                         seed = 6)
```

Next, we call the `generate_oc_plot` function, which will automatically generate the plots of operating characteristics. 

```{r}
plot <- generate_oc_plot(`3+3` = oc_3plus3,
                         `BOIN` = oc_boin,
                         `i3+3` = oc_i3plus3)
```

We can also save the plot the local directory using `ggsave` function from ggplot:
```{r}
# #Create a new directory named “Results”
# new.folder <- "Results"
# dir.create(file.path(mainDir, new.folder))
# #Create a new sub-directory named “Decision Tables”
# new.subfolder <- "Operating Characteristics"
# dir.create(file.path(mainDir, new.folder, new.subfolder))
# 
# ggsave(paste0(file.path(mainDir, new.folder, new.subfolder),"/oc_selection.jpg"),
#        width = 12,
#        height = 12,
#        plot[[1]])
# 
# ggsave(paste0(file.path(mainDir, new.folder, new.subfolder),"/oc_allocation.jpg"),
#        width = 12,
#        height = 12,
#        plot[[2]])
```

